---
title: "Kiva Data Science for Good"
output: html_notebook
---

# Kiva Data Science for Good

## Abstract
This anlaysis attempts to dig into the welfare level of Kiva borrowers around the world. This is done using a combination of Kiva loan data and external data sources.

## Rough Work
```{r}
library(tidyverse)
```


Load all the data
```{r}
kiva_loans <- read_csv("kiva_loans.csv")
kiva_mpi_region_locations <- read_csv("kiva_mpi_region_locations.csv")
loan_theme_ids <- read_csv("loan_theme_ids.csv")
loan_themes_by_region <- read_csv("loan_themes_by_region.csv")
```

Start exploring loan data
```{r}
summary(kiva_loans)
```

Interested in the differece between loan amount and funded amount
```{r}
kiva_loans %>% 
  group_by(funded_amount == loan_amount) %>% 
  summarise(count = n()) %>% 
  mutate(percent = count/sum(count))
  
```
Looks like most of the loans in this data set were fully funded.


Look into missing data
```{r}
sapply(kiva_loans, function(x) sum(is.na(x)))
```
Most of the data is there. Not tags for everyone but that is fine.


